Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-02-10 glsb.tex
quick edit
minor edits

@@

% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure*}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}, \citet{Kasparova14}, and this paper.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies.  For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars show the maximum detected stellar light radius.  These are all maximum detection radii, and thus should be considered lower limits.   \label{disk_comp}}
\end{figure*}

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. 
%Thanks to the observing specialists at Apache Point for their help executing our remote observations.

>>>>

\section{TO DO}
\begin{itemize}
\item{plug in numbers from Lauren's metallicity gradients}
  \item{expand discussion of Kasperova14}
\end{itemize}

@@

% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure*}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, gLSB \HI\ data from Malin 1 from \citet{Pickering97} and gLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.  Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.  For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.  These are all maximum detection radii, and thus should be considered lower limits.   \label{disk_comp}}
\end{figure*}

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
%Thanks to the observing specialists at Apache Point for their help executing our remote observations.
